Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-04-02 tese2/16_implementation_content.tex
[RFT] ui improvements
[ADD] spell checking, explained private network component at architecture

	In order to create content the user has the option to write simple movie captions without wrtting any code, otherwise, as mentioned before, it can write \ac{HTML}, \ac{CSS} and \emph{JavaScript}. The definition of the content's starting and ending time by the user it's not an easy task. Defining the content's time to appear in realtime would require a previous user plan. Otherwise the user could make a speech and add the content for later reproduction.

@@

\begin{minipage}{\linewidth}
\begin{lstlisting}[caption={Exampe of content created by one user},label={lst:createcontent},language=json]
{
	"cmd":"createContent",
	"start":"2016-03-29T03:56:40.000Z",
	"end":"2016-03-29T03:56:41.000Z",
	"content":"<h1>Hello</h1>"
}
\end{lstlisting}
\end{minipage}
	In order to help the content creator to show and synchronize its content in realtime we allow the user to encode its content into \emph{QR codes} and show it to the camera in real time.

	\ac{KMS} lets registring event handlers for \emph{QR code} detection. The component that detects \emph{QR codes} on \ac{KMS} is called periodically and fires the handlers with the decoded content. This mechanism does not detect if the \emph{QR code} enters or leaves the screen. We had to implement our own mechnism for detecting those events.

	Each user session in the server maintains a map with the contents that are present on the screen. In order to aplly our algorithm more efficiently we calculate the content's hash through the \emph{md5} method.

	If the hash is not present in the map it means the \emph{QR code} was entering the screen, we add that hash to the map and associate the current time to it, all the users are notified to watch that content in realtime. By doing an analogy to the \emph{Nyquist} theorem we know that if the same \emph{QR code} is not detected after a time bigger then two periods we can conclude that the \emph{QR code} leaved the screen and we add the correspondent content into our database. Listing \ref{lst:pseudo_qrcode} shows the pseudo code for \emph{QR code} leaving detection.

@@

	Multiple contents can be displayed at the same time, in order to achieve that, we define layers below the video with the same size. Each layer is associated to the content.

	We have taken into account that the amount of content tends to grow with time and the user should only have access to a subset of content instead all of them, which would be very ineficcient.

	The content to display for each user depends on the user's position on the timeline, this position is given by an offset between the current time and the navigated time. If the user is watchiing the content in realtime this offset is constant so there is no need to synchronize this value.

	Each content is divided into two components, the \emph{start} and the \emph{end} which are sent to users. The \emph{start} component contains a timestamp, the content identification number and the content itself in form of text. The \emph{end} component only contains the timestamp and the content identifcation number.

@@

	The content description messages that are sent to each user contains the contant itself on the form of a list of events and an atrtibute that specifies if the server has more content to return.

@@

	When a user enters the conference room, imediatelly after the \emph{WebSocket} creation the server sends him the current content.

	The user receives the content, sorts all components by time and creates a set of events. All the events before the user's time are rendered and removed from the set of events. A timer is schedulled for the first component on the event set and the process repeats while the set is not empty.

	If the set is empty, there two options, if the server contained more content a new request for content is made and the proccess starts from the beggining, namely the server sends the correpondent content again. If the server has no more content the process is stopped until it sends more.

@@

	Our solution is flexible on what kind of interactions are possible to the users in real time but allowing users to write \emph{Javascript} that is executed on the other users browser would attackers to misuse their resources and access to critical information.

@@

	By not allowing javascript we would need to implement all actions a priori and fire them when a type of message is received. We decided to ignore the security vulnarabilities that are exposed by evaluating \emph{javascript} because in order to offer the same interactions we would have to do an exaustive functionaly requirements gathering.

	Another way to solve this problem, which is not within the goals of this thesis, is to analyse the javascript code and detect if it is malicious.

@@

	We have used \emph{vis.js} to display out timeline. This library was created for content navigation through time, but it was not designed to be always moving automatically, we have created a background timer that performs the animation of moving the window of time bounds and user navigated time marker.

	Figure \ref{fig:timeline} shows the the graphic appearance of our interactive timeline, in order to navigate through time the user must drag and drop the timeline horizontaly, when the user drops the timeline an event handler is called with the new user's time offset which will be used to send a message to the server in order to choose the correspondent content to display.

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=\textwidth]{figures/timeline.png}
		\caption{Interactive timeline}
		\label{fig:timeline}
	\end{figure}

	We have noticed the server time being different from client time and this created graphic inconsistencies such as showing existing recorded blocks of movie in the future. To solve this problem the server sends its time to client imediately after the websocket creation, we synchronize the timeline with the server and although it may exist a small error due to network transmission time the graphical error is negligible.

@@

	Time annotations are simpler way save points in time and share them with other users. When a user enters in a conference room the server sends all annotations so they can be displayed directly into the user timeline. Each time annotation is created all users are advertised so they can update their interfaces.

	Figure \ref{fig:annotation} shows the creation and placement of annotations on the timeline, to save the annotation the user must click on the floppy icon in order to save it and advertise the conference participants.

@@

	Besides the ability to create tags it is also possible to create time hyperlinks, see figure \ref{fig:timelink}, that can be sent to other users externaly so they can navigate directly to the content when entering in the conference room.

@@

	Users can easily search for annotations and contents and travel to their correspondent times. In the case of hyper content after handling the result from database we ignore \ac{HTML} tags, extract the text with \emph{Jsoup}\footnote{\url{http://jsoup.org/} (Accessed 21 March 2016)} and apply the query again. We extract the text from \ac{HTML} because accidentatly searching for text contained in \ac{HTML} tags would lead to incorrect results.

>>>>

	In order to create content the user has the option to write simple movie captions without writing any code, otherwise, as mentioned before, it can write \ac{HTML}, \ac{CSS} and \emph{JavaScript}. The definition of the content's starting and ending time by the user it's not an easy task. Defining the content's time to appear in real-time would require a previous user plan. Otherwise the user could make a speech and add the content for later reproduction.

@@

\begin{minipage}{\linewidth}
\begin{lstlisting}[caption={Exampe of content created by one user},label={lst:createcontent},language=json]
{
	"cmd":"createContent",
	"start":"2016-03-29T03:56:40.000Z",
	"end":"2016-03-29T03:56:41.000Z",
	"content":"<h1>Hello</h1>"
}
\end{lstlisting}
\end{minipage}
	In order to help the content creator to show and synchronize its content in real-time we allow the user to encode its content into \emph{QR codes} and show it to the camera in real time.

	\ac{KMS} lets registering event handlers for \emph{QR code} detection. The component that detects \emph{QR codes} on \ac{KMS} is called periodically and fires the handlers with the decoded content. This mechanism does not detect if the \emph{QR code} enters or leaves the screen. We had to implement our own mechanism for detecting those events.

	Each user session in the server maintains a map with the contents that are present on the screen. In order to apply our algorithm more efficiently we calculate the content's hash through the \emph{md5} method.

	If the hash is not present in the map it means the \emph{QR code} was entering the screen, we add that hash to the map and associate the current time to it, all the users are notified to watch that content in real-time. By doing an analogy to the \emph{Nyquist} theorem we know that if the same \emph{QR code} is not detected after a time bigger then two periods we can conclude that the \emph{QR code} leaved the screen and we add the correspondent content into our database. Listing \ref{lst:pseudo_qrcode} shows the pseudo code for \emph{QR code} leaving detection.

@@

	Multiple contents can be displayed at the same time, in order to achieve that, we define layers above the video with the same size. Each layer is associated to the content.

	We have taken into account that the amount of content tends to grow with time and the user should only have access to a subset of content instead all of them, which would be very inefficient.

	The content to display for each user depends on the user's position on the time-line, this position is given by an offset between the current time and the navigated time. If the user is watching the content in real-time this offset is constant so there is no need to synchronize this value.

	Each content is divided into two components, the \emph{start} and the \emph{end} which are sent to users. The \emph{start} component contains a time stamp, the content identification number and the content itself in form of text. The \emph{end} component only contains the time stamp and the content identification number.

@@

	The content description messages that are sent to each user contains the constant itself on the form of a list of events and an attribute that specifies if the server has more content to return.

@@

	When a user enters the conference room, immediately after the \emph{WebSocket} creation the server sends him the current content.

	The user receives the content, sorts all components by time and creates a set of events. All the events before the user's time are rendered and removed from the set of events. A timer is scheduled for the first component on the event set and the process repeats while the set is not empty.

	If the set is empty, there two options, if the server contained more content a new request for content is made and the process starts from the beginning, namely the server sends the correspondent content again. If the server has no more content the process is stopped until it sends more.

@@

	Our solution is flexible on what kind of interactions are possible to the users in real time but allowing users to write \emph{JavaScript} that is executed on the other users browser would attackers to misuse their resources and access to critical information.

@@

	By not allowing \emph{JavaScript} we would need to implement all actions a priori and fire them when a type of message is received. We decided to ignore the security vulnerabilities that are exposed by evaluating \emph{JavaScript} because in order to offer the same interactions we would have to do an exhaustive functional requirements gathering.

	Another way to solve this problem, which is not within the goals of this thesis, is to analyze the \emph{JavaScript} code and detect if it is malicious.

@@

	We have used \emph{vis.js} to display out time-line. This library was created for content navigation through time, but it was not designed to be always moving automatically, we have created a background timer that performs the animation of moving the window of time bounds and user navigated time marker.

	Figure \ref{fig:timeline} shows the the graphic appearance of our interactive time-line, in order to navigate through time the user must drag and drop the time-line horizontally, when the user drops the time-line an event handler is called with the new user's time offset which will be used to send a message to the server in order to choose the correspondent content to display.

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=\textwidth]{figures/timeline.png}
		\caption{Interactive time-line}
		\label{fig:timeline}
	\end{figure}

	We have noticed the server time being different from client time and this created graphic inconsistencies such as showing existing recorded blocks of movie in the future. To solve this problem the server sends its time to client immediately after the \emph{webSocket} creation, we synchronize the time-line with the server and although it may exist a small error due to network transmission time the graphical error is negligible.

@@

	Time annotations are simpler way save points in time and share them with other users. When a user enters in a conference room the server sends all annotations so they can be displayed directly into the user time-line. Each time annotation is created all users are advertised so they can update their interfaces.

	Figure \ref{fig:annotation} shows the creation and placement of annotations on the time-line, to save the annotation the user must click on the floppy icon in order to save it and advertise the conference participants.

@@

	Besides the ability to create tags it is also possible to create time hyper-links, see figure \ref{fig:timelink}, that can be sent to other users externally so they can navigate directly to the content when entering in the conference room.

@@

	Users can easily search for annotations and contents and travel to their correspondent times. In the case of hyper content after handling the result from database we ignore \ac{HTML} tags, extract the text with \emph{Jsoup}\footnote{\url{http://jsoup.org/} (Accessed 21 March 2016)} and apply the query again. We extract the text from \ac{HTML} because accidentally searching for text contained in \ac{HTML} tags would lead to incorrect results.

### 2016-04-02 tese2/17_implementation_deploy.tex
[ADD] spell checking, explained private network component at architecture

\subsection{Software}
	INESC-ID provided us a restricted linux account without administration permissions, which we prevented us the installation of our solution directly on the machine because we would need administrative priviledges to install all the software that our solution depends on. Although that limitation, they provided access to Docker\footnote{\url{https://www.docker.com/} (Accessed March 27, 2016)} which run on host operating system as an isolated process in userspace.

	Inside a Docker container we have the administrative priviledges to install all the software dependencies.

	We could use one docker image for each component but in order to reduce the network usage we prefered to install all the components within the same image. At the same we provide an all-in-one easy to deploy solution as all the \ac{IP}s are local.

>>>>

\subsection{Software}
	\emph{INESC-ID} provided us a restricted \emph{Linux} account without administration permissions, which we prevented us the installation of our solution directly on the machine because we would need administrative privileges to install all the software that our solution depends on. Although that limitation, they provided access to Docker\footnote{\url{https://www.docker.com/} (Accessed March 27, 2016)} which run on host operating system as an isolated process in user space.

	Inside a Docker container we have the administrative privileges to install all the software dependencies.

	We could use one docker image for each component but in order to reduce the network usage we preferred to install all the components within the same image. At the same we provide an all-in-one easy to deploy solution as all the \ac{IP}s are local.

### 2016-04-02 tese2/architecture.tex
[ADD] spell checking, explained private network component at architecture

Taking into account the goals of this project and all the technology presented so far. Our proposal is the development of a web application that provides communication and collaboration in real-time.

@@

	Clients can discover chat rooms and other clients by querying the signaling server, they can create rooms for multi-party communication which is achieved by using \ac{WebRTC}'s \emph{MediaStream} and \emph{DataChannel}, namely for audio, video and text communication.

	Chat rooms can be public or private. Public chat rooms are moderated by a group of clients which initially is formed by the room creator, this type of room has no access restrictions by default, but that can be changed by its moderators. Private chat rooms will be visible for a list of clients or can be accessed by clients that have a link for that chat room.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/modules.pdf}
	\caption{System Modules}
        \label{fig:modules}
\end{figure}
%RP as figuras têm de ser apresentadas. Figure~\ref{fig:modules} presents ...
	Figure~\ref{fig:modules} presents the structure of our system which is divided into six modules:

@@

\section{Implementation Proposal}
The infrastructure is composed by: Ice Server, Web Server, Stream Server, Signaling Server and Test Clients.

@@

In order to simplify our solution, we propose both the \emph{Application} and \emph{Signaling} modules implementation within the same server application so it could be easy to control which resources the client has permission to access.

We have taken into account the compatibility between the streaming server, database and the operation transformation solutions in order choose the appropriate framework to implement our web server.

Based on our study about signaling protocols we decided to exclude \ac{XMPP} due to the development difficulties that it exposes when using multiple web pages, namely the user re-authentication performed each time a page is loaded and the single tab usage limitation. By consequence we have not choosen \emph{Jitsi Video Brigde} as it uses \ac{XMPP}.

By excluding \emph{Jitsi Video Brigde} we have decided that our solution must use \ac{KMS}. Our web server could be implemented more easily with \emph{NodeJS} or \emph{Java} due to the fact \ac{KMS} provides clients for both technologies but others could be used as \ac{KMS} also exposes their \ac{API} via \emph{WebSockets}.

@@

For the web server we could choose \emph{NodeJS} or any \emph{Java} based web framework. One of our criteria for choosing the web framework is the ability to follow the \ac{MVC} paradigm which can help us to organize our code. Without any strong reason we have decided to implement our webserver with \emph{PlayFramework}\footnote{\url{https://www.playframework.com/}(acessed March 25, 2016)} using \emph{Java}.

For the collaborative text editor, we have choosen \emph{OT.js} due to its indenpendence from server implementation and storage choice.

For the \emph{NAT Traversal} module an \ac{ICE} server is not required to be on our infrastructure, as a public \ac{STUN} server can be used for testing our solution.

On the client computers, both \emph{Mozilla Firefox} and \emph{Google Chrome} should be installed as web browsers. Libraries such as \emph{jQuery}, \emph{Bootstrap}, \emph{Adapter.js}, \emph{OT.js} can be downloaded from the Web Server and executed on the client side.

@@

Figure~\ref{fig:apparch} presents the application architecture and the underlying technologies. \emph{Adapter.js} and \emph{jQuery} will ensure that our application is compatible with the most popular web browsers.
\emph{Bootstrap} will be used to make the user interface more appellative and responsive. With \emph{Bootstrap} it is quite easy to develop applications that adapt to mobile devices with different screen sizes.

>>>>

Taking into account the goals of this project and all the technology presented so far. Our proposal is the development of a web application that provides communication and collaboration features in real-time.

@@

	Moreover we allow clients to discover chat rooms and other clients by navigating on the web pages provided by our web server. In addition users can create rooms for multi-party audio and video communication communication which is achieved by using \ac{WebRTC}'s \emph{MediaStream} and \emph{PeerConnection}.

	Furthermore, chat rooms can be public or private. Public chat rooms are moderated by a group of clients which initially is only the room creator, this type of room has no access restrictions by default, but that can be changed by its moderators. Private chat rooms will be visible for a defined list of clients or can be accessed by clients that have a link for that conference room.

@@

	In this section we present the modules of our application.

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/modules.pdf}
	\caption{System Modules}
        \label{fig:modules}
\end{figure}
%RP as figuras têm de ser apresentadas. Figure~\ref{fig:modules} presents ...
	Figure~\ref{fig:modules} presents the structure of our system which is divided into six modules:

@@

\section{Implementation Proposal}
The infrastructure is composed by: web server, stream server, signaling server, database and video repository.

@@

In order to simplify our solution, we propose both the \emph{Application}, \emph{Signaling}, \emph{Stream} and \emph{Storage} modules implementation within the same server application so it could be easy to deploy as a single image. To this set of modules we often call \emph{backend}.

Having established that the \emph{backend} modules are placed in the same machine, that helps controlling which resources the client has permission to access as those modules are seen as a private network.

To qualify the above we provide public access to \ac{HTTP} server ports, maintaining the access to other components restricted through firewall rules. In relation to the database there is no directly access from outside, all the database information is accessed via our application server which validates the permissions of users when acting above our system.

On the other hand, the access to our streaming servers is also restricted but clients can connect to them after concluding the signaling phase. This signaling phase may or not proceed in function of the client access permissions, for example if a user is trying to access a private conference room that is not member of or has no invitation link, the signaling server rejects to start the signaling phase and the user cannot access to the streaming server.

Furthermore, we have taken into account the compatibility between the streaming server, database and the operation transformation solutions in order choose the appropriate framework to implement our web server.

As a result of our study about signaling protocols we have decided to exclude \ac{XMPP} due to the development difficulties that it exposes when using multiple web pages, namely the user re-authentication performed each time a page is loaded and the single tab usage limitation. By consequence we have not chosen \emph{Jitsi Video Brigde} as it uses \ac{XMPP}.

Accordingly, by excluding \emph{Jitsi Video Brigde} we have decided that our solution must use \ac{KMS}. Our web server could be implemented easily with \emph{NodeJS} or \emph{Java} due to the fact \ac{KMS} provides clients for both technologies but others could be used as \ac{KMS} also exposes their \ac{API} via \emph{WebSockets}.

@@

Due to the fact we are going to use \ac{KMS} as streaming server solution, we could choose \emph{NodeJS} or any \emph{Java} based web framework for implementing our web application server. One of our criteria for choosing the web framework is the ability to follow the \ac{MVC} paradigm which can help us to organize our code. Without any strong reason we have decided to implement our web server with \emph{PlayFramework}\footnote{\url{https://www.playframework.com/}(acessed March 25, 2016)} using \emph{Java}.

Importantly, for the collaborative text editor, we have chosen \emph{OT.js} due to its server and storage implementation choice independence.

For the \emph{NAT Traversal} module an \ac{ICE} server is not required to be on our infrastructure, as a public \ac{STUN} server can be used for testing our solution although we recognize that for a production environment we would need to maintain our own \ac{TURN} servers in order to ensure connectivity to all clients.

Not less important, on the client computers, both \emph{Mozilla Firefox} and \emph{Google Chrome} should be installed as web browsers. Libraries such as \emph{jQuery}, \emph{Bootstrap}, \emph{Adapter.js}, \emph{OT.js} can be downloaded from the web server and executed on the client side.

@@

Figure~\ref{fig:apparch} presents the application architecture and the underlying technologies seen from the user's perspective. \emph{Adapter.js} and \emph{jQuery} will ensure that our application is compatible with the most popular web browsers.
\emph{Bootstrap} will be used to make the user interface more appellative and responsive. With \emph{Bootstrap} it is quite easy to develop applications that adapt to mobile devices with different screen sizes.

### 2016-04-02 tese2/evaluation.tex
[ADD] spell checking, explained private network component at architecture

  In this chapter we describe how we tested our solution, show and analyse the results in order to validate the contributions of this thesis.

@@

\section{Tests Scenarios}

  In this section we describe both performance and usability test scenarios that we have applied.

  \subsection {Performance Tests}
      In order to benchmark our system, we have implemented a small \emph{Python} script using \emph{psutil}\footnote{\url{https://github.com/giampaolo/psutil} (Accessed March 27, 2016)} that collects with a periodicity of one second; CPU, physical memory information realtive to each running process and network usage relative to each interface.

@@

  \subsection {Usability Tests}

@@

      \item Enter in the conference room correspondent to the fourth task by sharing your camera and create a time annotaion in the instant of time when you entered, navigate to the current time, search for the annotation and leave the conference room.

@@

      The fourth task is used to analyse the behaviour and difficulties of the user when creating a time annotation.

@@

\section{Test Results}
  \subsection {Performance Tests}

      From the media server prespective if there are $n$ clients connected each of them sending and receiving one stream, it is expected that server sends and receives also $n$ streams. By so we expect that the amount of network increases lineraly as users join a confrence room.

      The blue peaks are caused by the signaling phase and web page downloads, including resources such as images, stylesheets and javascript files. 
      The green peaks are caused by that being transfered between \ac{KMS} and \emph{MongoDB} through \emph{Kurento Repository} each peak occurs each time a block of video is recorded which in this case is every ten seconds. 
      The recordings are synchronized so all user and mixed blocks starts and ends at the same time, that's why the amount of work done every ten seconds acumulates and because this is poerformed locally the maximum transfer rate is limited by the performance of the memory as buffers are writen to buffers then to disks. 
      Client's sent data transfer rate has no significant peaks as signaling information contains few information.

Figure \ref{fig:test_full_features_mem} shows the memory usage during our performance test case. Both \ac{JVM}, \emph{MongoDB} and \ac{KMS} performs their own memory management by holding and recycling objects when needed. The expected and observed behaviour of the memory usage is growth memory usage while the users are entering in the conference room and a memory usage stabilization aftwerwards.

\emph{MongoDB} memory usage keeps increasing because it trys to fit part of the database on \ac{RAM} for fast read access. \emph{MongoDB} checkpoints data to disk every 60 seconds or when journal data exceeds 2GB\footnote{\url{https://docs.mongodb.org/manual/faq/storage/}(Accessed March 28, 2016)}, that explains the small memory usage peaks during our test case. When the conference room is empty no there are no video recordings, which explains the memory stabilization at the end.

Figure \ref{fig:test_full_features_cpu_zoom} is the same as figure \ref{fig:test_full_features_cpu} but zoomed over \emph{MongoDB}, \emph{Java} and \emph{Kurento Repository}. As we can see there are periodic proccessing peaks every ten seconds that are due to block recording.

We conclude that \emph{QR code} detection is a very intensive task, approximately doubling the amount of work performed by \ac{CPU}. Without this feature the network and memory usage had insignificate changes compared to \ac{CPU} usage.

  \subsection {Usability Tests}

@@

On the second task one user clicked on the friends list for adding a friend to room and by consequence made him leave the conference room to the user profile. We solved this problem by showing a popup with the user profile and an additional button to add the user to the conference room as it can be seen on figure \ref{fig:test_ui_04}.

@@

On the third task we noticed that both users were not expecting to search the content directly from the search bar, instead they used the timeline.

On the fourth task both users didn't placed their annotations on wright place, we only provide one way to place annotations, which is by dragging them on the timeline. 
After creating an annotation users also didn't understand that they had to save their changes on the timeline, we solved this problem by saving automatically each time the user changed any annotation, the old user interface can be seen on figure \ref{fig:test_ui_05}.

@@

\begin{itemize}
\item Giving feedback to user when saving content and collaborative editors.
\item Support file upload on our chat.
\item Starting with our timeline more zoomed in order to give more sensation of time.
\item Create content with starting time and duration insted ending time.
\end{itemize}

>>>>

  In this chapter we describe how we tested our solution, show and analyze the results in order to validate the contributions of this thesis.

@@

  \section {Performance Tests}

     In this section we describe performance test scenarios that we have applied and their respective results.

    \subsection{Tests Scenarios}

      In order to benchmark our system, we have implemented a small \emph{Python} script using \emph{psutil}\footnote{\url{https://github.com/giampaolo/psutil} (Accessed March 27, 2016)} that collects with a periodicity of one second; CPU, physical memory information relative to each running process and network usage relative to each interface.

@@

\subsection{Test Results}

      From the media server prespective if there are $n$ clients connected each of them sending and receiving one stream, it is expected that server sends and receives also $n$ streams. By so we expect that the amount of network increases linearly as users join a conference room.

      The blue peaks are caused by the signaling phase and web page downloads, including resources such as images, stylesheets and javascript files. 
      The green peaks are caused by that being transfered between \ac{KMS} and \emph{MongoDB} through \emph{Kurento Repository} each peak occurs each time a block of video is recorded which in this case is every ten seconds. 
      The recordings are synchronized so all user and mixed blocks starts and ends at the same time, that's why the amount of work done every ten seconds accumulates and because this is performed locally the maximum transfer rate is limited by the performance of the memory as buffers are written to buffers then to disks. 
      Client's sent data transfer rate has no significant peaks as signaling information contains few information.

Figure \ref{fig:test_full_features_mem} shows the memory usage during our performance test case. Both \ac{JVM}, \emph{MongoDB} and \ac{KMS} performs their own memory management by holding and recycling objects when needed. The expected and observed behavior of the memory usage is growth memory usage while the users are entering in the conference room and a memory usage stabilization afterwards.

\emph{MongoDB} memory usage keeps increasing because it tries to fit part of the database on \ac{RAM} for fast read access. \emph{MongoDB} checkpoints data to disk every 60 seconds or when journal data exceeds 2GB\footnote{\url{https://docs.mongodb.org/manual/faq/storage/}(Accessed March 28, 2016)}, that explains the small memory usage peaks during our test case. When the conference room is empty no there are no video recordings, which explains the memory stabilization at the end.

Figure \ref{fig:test_full_features_cpu_zoom} is the same as figure \ref{fig:test_full_features_cpu} but zoomed over \emph{MongoDB}, \emph{Java} and \emph{Kurento Repository}. As we can see there are periodic processing peaks every ten seconds that are due to block recording.

We conclude that \emph{QR code} detection is a very intensive task, approximately doubling the amount of work performed by \ac{CPU}. Without this feature the network and memory usage had insignificant changes compared to \ac{CPU} usage.

\section {Usability Tests}
     In this section we describe usability test scenarios that we have applied and their respective results.

    \subsection{Tests Scenarios}

@@

      \item Enter in the conference room correspondent to the fourth task by sharing your camera and create a time annotation in the instant of time when you entered, navigate to the current time, search for the annotation and leave the conference room.

@@

      The fourth task is used to analyse the behavior and difficulties of the user when creating a time annotation.

@@

  \subsection{Test Results}

@@

On the second task one user clicked on the friends list for adding a friend to room and by consequence made him leave the conference room to the user profile. We solved this problem by showing a pop-up with the user profile and an additional button to add the user to the conference room as it can be seen on figure \ref{fig:test_ui_04}.

@@

On the third task we noticed that both users were not expecting to search the content directly from the search bar, instead they used the time-line.

On the fourth task both users didn't placed their annotations on wright place, we only provide one way to place annotations, which is by dragging them on the time-line. 
After creating an annotation users also didn't understand that they had to save their changes on the time-line, we solved this problem by saving automatically each time the user changed any annotation, the old user interface can be seen on figure \ref{fig:test_ui_05}.

@@

\begin{itemize}
\item Giving feedback to user when saving content and collaborative editors.
\item Support file upload on our chat.
\item Starting with our time-line more zoomed in order to give more sensation of time.
\item Create content with starting time and duration instead ending time.
\end{itemize}
